Parsing Postfix log files

### 2009-04-04 doc/logparser-results.tex
Further improvement to the explanation of better parsing performance for mail loops.

% XXX IS CHANGING FIGURE TO GRAPH A GOOD IDEA?
\renewcommand{\figurename}{Graph}

@@

An important property of a parser is how parsing time scales relative to
input size: does it scale linearly, polynomially, or exponentially?
\Graphref{parsing time vs file size vs number of log lines graph} shows the
parsing time in seconds, file size in MB, and number of log lines in tens
of thousands, for each of the \numberOFlogFILES{} log files.  The three
lines run roughly in parallel, giving the impression that the algorithm
scales linearly with input size.  This impression is borne out by
\graphref{parsing time vs file size vs number of log lines factor}, which
plots both the ratio of file size vs parsing time, and the ratio of number
of log lines vs parsing time (higher is better in both cases);
\tableref{parsing time vs file size vs number of log lines factor table}
shows the same ratios for different groups of log files.  The ratios are
quite tightly banded, showing that the algorithm scales linearly; the
ratios increase (i.e.\ improve) for log files 22 and 62--68, despite their
larger than average size.  In both groups of log files there was a mail
loop because a user set up mail forwarding incorrectly, resulting in a very
different distribution of log lines: normally most log lines are generated
by mail delivery attempts from other hosts, but when the mail loops
occurred most of the log lines resulted from failed delivery of mail
generated on the server itself.  The Postfix components that generated most
of the log lines during the mail loop have fewer associated rules than the
Postfix components whose log lines normally make up the bulk of each log
file; \graphref{Average number of rules tried per log line} shows the drop
in the average number of rules tried per log line for log files containing
a mail loop.

@@

\showgraph{build/graph-average-number-of-rules-tried-per-program}{Average
number of rules tried per Postfix component per log line}{Average number of
rules tried per Postfix component per log line}

>>>>

\renewcommand{\figurename}{Graph}

@@

An important property of a parser is how parsing time scales relative to
input size: does it scale linearly, polynomially, or exponentially?
\Graphref{parsing time vs file size vs number of log lines graph} shows the
parsing time in seconds, file size in MB, and number of log lines in tens
of thousands, for each of the \numberOFlogFILES{} log files.  The three
lines run roughly in parallel, giving the impression that the algorithm
scales linearly with input size.  This impression is borne out by
\graphref{parsing time vs file size vs number of log lines factor}, which
plots both the ratio of file size vs parsing time, and the ratio of number
of log lines vs parsing time (higher is better in both cases);
\tableref{parsing time vs file size vs number of log lines factor table}
shows the same ratios for different groups of log files.  The ratios are
quite tightly banded, showing that the algorithm scales linearly; the
ratios increase (i.e.\ improve) for log files 22 and 62--68, despite their
larger than average size.  Both groups of log files are much larger than
usual due to a mail loop caused by a user who set up mail forwarding
incorrectly, resulting in a very different distribution of log lines:
normally most log lines are generated by mail delivery attempts from other
hosts, but when the mail loops occurred most of the log lines resulted from
failed delivery of mail generated on the server itself.  The Postfix
components that generated most of the log lines during the mail loop have
fewer associated rules than the Postfix components whose log lines normally
make up the bulk of each log file, so the average number of rules tried per
log line reduces and so does the average parsing time per log line.
\Graphref{Average number of rules tried per log line} shows the drop in the
average number of rules tried per log line for log files containing a mail
loop, and \graphref{Average number of rules tried per log line for each
Postfix component} shows the average number of rules tried per log line for
each Postfix component.

@@

\showgraph{build/graph-average-number-of-rules-tried-per-program}{Average
number of rules tried per log line for each Postfix component}{Average
number of rules tried per log line for each Postfix component}
